\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=22mm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=black,
  citecolor=black,
  pdfborder={0 0 0}
}

\newcommand{\ghurl}{https://github.com/goldkiss2010-ai/conj-preprint}
\newcommand{\preprintver}{v0.9}
\newcommand{\preprintdate}{2026-02}
\newcommand{\repotag}{v0.1-smoke-ok}
\newcommand{\authornameen}{Bungaku Yokota}
\newcommand{\authornamejp}{横田ブンガク}

\begin{document}
\thispagestyle{empty}

{\Large \bfseries Preprint Notice / プレプリント告知}\par
\vspace{0.9em}

{\bfseries Preprint Notice}\par
{\bf EN}\quad This document is a self-published preprint.\par
\hspace*{2.2em}It has not undergone peer review and is not published in any academic journal.\par
\vspace{0.4em}
{\bf JP}\quad 本稿は自己公開されたプレプリントであり、査読を経た学術誌論文ではありません。\par

\vspace{1.1em}

{\bfseries Copyright \& License (Paper) / 著作権とライセンス（本文）}\par
{\bf EN}\quad Copyright \textcopyright\ 2026 \authornameen.\par
\hspace*{2.2em}This preprint is licensed under Creative Commons Attribution 4.0 (CC BY 4.0).\par
\vspace{0.4em}
{\bf JP}\quad 著作権 \textcopyright\ 2026 \authornamejp.\par
\hspace*{2.2em}本プレプリント（本文）は CC BY 4.0（表示 4.0 国際）により提供されます。\par

\vspace{1.1em}

{\bfseries Code Availability \& License / 実装公開とライセンス}\par
{\bf EN}\quad A reference implementation and experimental code corresponding to this manuscript\par
\hspace*{2.2em}are publicly available at:\par
\hspace*{2.2em}{\bf GitHub:} \href{\ghurl}{\ghurl}\par
\hspace*{2.2em}The code is licensed under the Apache License, Version 2.0 (Apache-2.0).\par
\vspace{0.4em}
{\bf JP}\quad 本稿に対応する参照実装および実験コードは、以下のリポジトリにて公開しています。\par
\hspace*{2.2em}{\bf GitHub:} \href{\ghurl}{\ghurl}\par
\hspace*{2.2em}コードのライセンスは Apache License, Version 2.0（Apache-2.0）です。\par
\hspace*{2.2em}詳細はリポジトリ内の \texttt{LICENSE} 等をご参照ください。\par

\vspace{1.1em}

{\bfseries Disclaimer / 免責}\par
{\bf EN}\quad The author makes no warranties regarding the correctness, completeness,\par
\hspace*{2.2em}or fitness for any particular purpose of this manuscript or the accompanying code.\par
\vspace{0.4em}
{\bf JP}\quad 本稿および付随する実装の内容について、著者はいかなる正確性・完全性・\par
\hspace*{2.2em}特定目的への適合性も保証しません。\par

\vspace{0.9em}

{\bfseries Intellectual Property / 知的財産に関する注意}\par
{\bf EN}\quad No FTO (freedom-to-operate) search is provided here.\par
\hspace*{2.2em}Nothing in this preprint or the accompanying code should be construed as legal advice.\par
\vspace{0.4em}
{\bf JP}\quad 本稿および付随資料は、FTO（Freedom-to-Operate：実施自由度）調査を提供するものではありません。\par
\hspace*{2.2em}本稿の記載は法的助言を構成しません。\par

\vspace{1.1em}

{\bfseries Version Information / バージョン情報}\par
{\bf EN}\quad Preprint version: \preprintver\quad\textbar\quad Date: \preprintdate\par
{\bf EN}\quad Reproducibility repo: \href{\ghurl}{\ghurl}\quad\textbar\quad Tag: \repotag\par
{\bf JP}\quad プレプリント版：\preprintver\quad\textbar\quad 作成日：\preprintdate\par
{\bf JP}\quad 再現用リポジトリ：\href{\ghurl}{\ghurl}\quad\textbar\quad タグ：\repotag\par

\end{document}
